I don't know, are you sure we want to do this?\\ Sea level adaptation decisions under uncertainty

### 2016-12-29 submission/paper.tex
sync

We project local sea level changes by Modeling two processes, the relationship between global temperature and global sea level, and the relationship between global sea level and local sea level.

@@

\subsection{Damage costs}

>>>>

We project local sea level changes by modeling two processes, the relationship between global temperature and global sea level, and the relationship between global sea level and local sea level.

@@

\subsection{Damage costs}
A simplistic analysis of projected damage costs, not taking into account the uncertainty, would use  the median  historical damage cost multiplied by  the median damage factor at 2100 at the median sea level rise projected for 2100.
